\documentclass[12pt]{article}
% packages
\usepackage[a4paper, margin=1in]{geometry}

\title{\vspace{3cm}Egyptian Fitness Market Analysis}
\author{by Youssif Hamed}
\date{}

\begin{document}
\maketitle  
\date
\newpage

\tableofcontents
\newpage
\section{Introduction}
This report aims to explore the fitness and healthy food market in Egypt to descover potential opportunites. The report is mainly focused on the Gym and online training not all sports in general. The Data used in this report is collected from a survey, Google maps, food delivery apps, online training platforms, and online shopping platforms.

\subsection{Quesions to be answered}
The main questions that this report aims to answer are:
\begin{enumerate}
    \item How much of the population is interested in fitness and healthy food?
    \item What are the main demographics of people interested in fitness and healthy food?
    \item Does investing in the people knowledge about fitness and healthy food help in increasing the sales?
    \item Is there is a need to healthy food services in Egypt
    \item Do the current market players satisfy the market needs?
    \item Do people trust online training platforms?
    \item What is the average cost of the online training services?
    \item What people think online training platforms should cost?
    \item Is there enough gyms in Egypt?
    \item What is the average cost of gym memberships?
    \item Does people trust supplements?
    \item what is the most used supplement?
\end{enumerate}
\end{document}